Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-02-02 R0V0.tex
Remove the scaled diagonal dominance paragraphs

\mypara To that end three methodologies are recalled below: chordal graphs, scaled diagonal dominance and alternating direction of multipliers (ADMM). The first exploits the network topology to decompose it into smaller complete components. The second method exploits the stability of individual agents (i.e., when these considered not connected to the network) and weak coupling. Finally, the last method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality (see Eq.~\eqref{eq:Artstein-Sontag:inequality:dual}, below). Note that these methodologies can be used either separately or together. The latter would appropriate, when the smaller components of the network still have a large number of states and the computing platform where the solver runs has memory limitations.

@@

\mypara Let $\mathscr{C}$ be a clique of the graph $\mathscr{G}$ and consider the corresponding matrix $F$ that must satisfy the MI~\eqref{eq:MIF}. If the vector fields $f$ and $B$ are polynomials and the search for the matrix $F$ is restricted to have appropriate diagonal structure, then the negative definiteness can be shown using the optimization method proposed in \cite{AhmadiHall2016}.

\mypara A matrix $D\in\mathbb{R}^{h\times h}$ is said to be \emph{diagonally dominant} (dd) if, for every index $i\in\mathbb{N}_{[1,h]}$, the inequality $|D_{ii}|\geq\sum_{i=1}^h |D_{ij}|$ holds. It is said to be \emph{scalable diagonally dominant} (sdd) if there exists a diagonal matrix $\overline{D}\in\mathbb{R}_{\geq0}^{h\times h}$ such that $\overline{D}D\overline{D}$ is diagonally dominant.

\mypara The set of scalable diagonally dominant matrices is denoted by $SDD_h$. Let
		\begin{align*}
			\mathbf{SDD}(U)=\{P\succ0,P\in\mathbb{R}^{h\times h}:P=U^\top DU,\\
			 D\in SDD_h\}
		\end{align*}
be the set of positive definite matrices parameterized by a matrix $U\in\mathbb{R}^{h\times h}$.

\mypara Whenever the matrix $A$ is scalable diagonally dominant and the choice for $Y$ preserves this structure, the MI~\eqref{eq:MIF} can be relaxed into the following sum-of-squares feasibility program:
\begin{subequations}
\begin{equation}\label{eq:DSOS}
\begin{array}{rcl}
-F_l&\in&\mathbf{SDD}(U_l)\;,
\end{array}
\end{equation}
where the sequence $\{U_l\}_{l\in\mathbb{N}}\subset\mathbb{R}^{h\times h}$ is defined as
\begin{equation}
\begin{array}{rcl}
	U_0&=&\ I_h\\
	U_{l+1}&=&\mathbin{\mathtt{chol}}(F_l)\;.
\end{array}
\end{equation}
\end{subequations}
Note that, the requirement of $A$ to be diagonally dominant can be interpreted as the network having stable agents interconnected with a weak coupling.

>>>>

\mypara To that end two methodologies are recalled below: chordal graphs and alternating direction of multipliers (ADMM). The first exploits the network topology to decompose it into smaller complete components. The last method is based on the search of the metric over two sets of matrices: uniformly positive definite matrices and matrices satisfying a specific matrix inequality (see Eq.~\eqref{eq:Artstein-Sontag:inequality:dual}, below). The latter would appropriate, when the smaller components of the network still have a large number of states and the computing platform where the solver runs has memory limitations.

@@
